\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-27 Writeup/paper.tex
Add ISP-specific data and some discussion

We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.
Below are the results of each run, averaged across ISPs:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
  & Popular Youtube   & 60  & 14  & 14  \\ \hline
  & Soundcloud        & 161 & 162 & 184 \\ \hline
  & Twitch.tv         & 198 & 159 & 172 \\ \hline
2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
  & Popular Youtube   & 63  & 14  & 31  \\ \hline
  & Soundcloud        & 161 & 160 & 165 \\ \hline
  & Twitch.tv         & 193 & 159 & 181 \\ \hline
3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
  & Popular Youtube   & 31  & 23  & 18  \\ \hline
  & Soundcloud        & 179 & 171 & 160 \\ \hline
  & Twitch.tv         & 184 & 159 & 161 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 14 & 14 & 15 \\ \hline
2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 12 \\ \hline
3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 13 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput (KB/s): \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 197.8 \\ \hline
  & Popular Youtube   & 202.6 \\ \hline
  & Soundcloud        & 197.9 \\ \hline
  & Twitch.tv         & 201.2 \\ \hline
2 & Unpopular Youtube & 201.9 \\ \hline
  & Popular Youtube   & 197.8 \\ \hline
  & Soundcloud        & 201.3 \\ \hline
  & Twitch.tv         & 203.1 \\ \hline
3 & Unpopular Youtube & 202.8 \\ \hline
  & Popular Youtube   & 200.4 \\ \hline
  & Soundcloud        & 203.6 \\ \hline
  & Twitch.tv         & 204.9 \\ \hline
\end{tabular}

@@

@@

\subsubsection{Test case 2}
The second test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
The results are tabulated below:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 4   & 19  & 188 \\ \hline
  & Popular Youtube   & 4   & 19  & 21  \\ \hline
  & Twitch.tv         & 148 & 154 & 148 \\ \hline
  & Soundcloud        & 148 & 148 & 0   \\ \hline
2 & Unpopular Youtube & 3   & 47  & 19  \\ \hline
  & Popular Youtube   & 4   & 20  & 19  \\ \hline
  & Twitch.tv         & 172 & 154 & 0   \\ \hline
  & Soundcloud        & 148 & 149 & 149 \\ \hline
3 & Unpopular Youtube & 4   & 33  & 19  \\ \hline
  & Popular Youtube   & 3   & 20  & 18  \\ \hline
  & Twitch.tv         & 149 & 148 & 0   \\ \hline
  & Soundcloud        & 148 & 148 & 148 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 190.9   \\ \hline
  & Popular Youtube   & 8048.6  \\ \hline
  & Twitch.tv         & 10526.7 \\ \hline
  & Soundcloud        & 1341.4  \\ \hline
2 & Unpopular Youtube & 9513.0  \\ \hline
  & Popular Youtube   & 8335.4  \\ \hline
  & Twitch.tv         & 11397.1 \\ \hline
  & Soundcloud        & -       \\ \hline
3 & Unpopular Youtube & 9840.6  \\ \hline
  & Popular Youtube   & 7260.2  \\ \hline
  & Twitch.tv         & 11274.2 \\ \hline  
  & Soundcloud        & -       \\ \hline
\end{tabular}

>>>>

We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.

\subsubsection{Results across ISPs}
Below are the results of each run, averaged across ISPs:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
  & Popular Youtube   & 60  & 14  & 14  \\ \hline
  & Soundcloud        & 161 & 162 & 184 \\ \hline
  & Twitch.tv         & 198 & 159 & 172 \\ \hline
2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
  & Popular Youtube   & 63  & 14  & 31  \\ \hline
  & Soundcloud        & 161 & 160 & 165 \\ \hline
  & Twitch.tv         & 193 & 159 & 181 \\ \hline
3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
  & Popular Youtube   & 31  & 23  & 18  \\ \hline
  & Soundcloud        & 179 & 171 & 160 \\ \hline
  & Twitch.tv         & 184 & 159 & 161 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 14 & 14 & 15 \\ \hline
2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 12 \\ \hline
3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 13 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput (KB/s): \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 197.8 \\ \hline
  & Popular Youtube   & 202.6 \\ \hline
  & Soundcloud        & 197.9 \\ \hline
  & Twitch.tv         & 201.2 \\ \hline
2 & Unpopular Youtube & 201.9 \\ \hline
  & Popular Youtube   & 197.8 \\ \hline
  & Soundcloud        & 201.3 \\ \hline
  & Twitch.tv         & 203.1 \\ \hline
3 & Unpopular Youtube & 202.8 \\ \hline
  & Popular Youtube   & 200.4 \\ \hline
  & Soundcloud        & 203.6 \\ \hline
  & Twitch.tv         & 204.9 \\ \hline
\end{tabular}

@@

\subsubsection{Results across runs}
To investigate the differences between ISPs, we present below the offset from the median ping and throughput averaged across the 3 runs:
\vspace{1em} \\
Offset from median ping to website (ms, lower is better): \\
\begin{tabular}{|l|c|c|c|c|c|} \hline
 & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
\small{Unpopular YT} & 9  & 23  & 2  & -1  & -3 \\ \hline
Popular YT           & 11 & 88  & 1  & -1  & -6 \\ \hline
Soundcloud           & 10 & 0   & -5 & -3  & 53 \\ \hline
Twitch.tv            & 26 & 6   & 14 & -9  & 41 \\ \hline
Total                & 56 & 117 & 12 & -14 & 85 \\ \hline
\end{tabular}
\vspace{1em} \\
Offset from median ping to CDN (ms, lower is better): \\
\begin{tabular}{|l|c|c|c|c|c|} \hline
 & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
\small{Unpopular YT} & 35 & -1 & 0  & -2 & 21 \\ \hline
Popular YT           & 0  & 0  & 0  & -2 & 28 \\ \hline
Soundcloud           & 14 & 2  & -6 & -1 & 25 \\ \hline
Twitch.tv            & -5 & -4 & 1  & 1  & 12 \\ \hline
Total                & 44 & -4 & -4 & -3 & 86 \\ \hline
\end{tabular}
\vspace{1em} \\
Offset from median ping to content (ms, lower is better): \\
\begin{tabular}{|l|c|c|c|c|c|} \hline
 & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
\small{Unpopular YT} & -5  & -5 & 3  & 56 & 15 \\ \hline
Popular YT           & 0   & 7  & 0  & -2 & 45 \\ \hline
Soundcloud           & -8  & -1 & 2  & -1 & 52 \\ \hline
Twitch.tv            & 0   & 29 & -3 & 15 & 16 \\ \hline
Total                & -14 & 29 & 2  & 68 & 129 \\ \hline
\end{tabular}
\vspace{1em} \\
Offset from median throughput (KB/s, higher is better): \\
\begin{tabular}{|l|c|c|c|c|c|} \hline
 & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
\small{Unpopular YT} & 1.5  & -0.5  & 2.1   & -3.9 & -2.9 \\ \hline
Popular YT           & -0.8 & -8.5  & -3.1  & 0.4  & -1.2 \\ \hline
Soundcloud           & 0.1  & -5.1  & -1.3  & 2.5  & -5.4 \\ \hline
Twitch.tv            & -0.4 & 0.3   & -6.8  & 0.7  & -0.6 \\ \hline
Total                & 0.4  & -13.8 & -9.2  & -0.3 & -10.2\\ \hline
\end{tabular}
\vspace{1em} \\
While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping, although still less than 100ms, suggesting that the caches for WebAfrica are still within South Africa but not in Cape Town (for example, they could be in Johannesburg). The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.

@@

\subsubsection{Test case 2}
The second test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
The results are tabulated below:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 4   & 19  & 188 \\ \hline
  & Popular Youtube   & 4   & 19  & 21  \\ \hline
  & Twitch.tv         & 148 & 154 & 148 \\ \hline
  & Soundcloud        & 148 & 148 & 0   \\ \hline
2 & Unpopular Youtube & 3   & 47  & 19  \\ \hline
  & Popular Youtube   & 4   & 20  & 19  \\ \hline
  & Twitch.tv         & 172 & 154 & 0   \\ \hline
  & Soundcloud        & 148 & 149 & 149 \\ \hline
3 & Unpopular Youtube & 4   & 33  & 19  \\ \hline
  & Popular Youtube   & 3   & 20  & 18  \\ \hline
  & Twitch.tv         & 149 & 148 & 0   \\ \hline
  & Soundcloud        & 148 & 148 & 148 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\ % TODO: Update these with correct values
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
  & Popular Youtube   & 9 & 9 & 9 \\ \hline
  & Twitch.tv         & 9 & 9 & 9 \\ \hline
  & Soundcloud        & 9 & 9 & 1 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 190.9   \\ \hline
  & Popular Youtube   & 8048.6  \\ \hline
  & Twitch.tv         & 10526.7 \\ \hline
  & Soundcloud        & 1341.4  \\ \hline
2 & Unpopular Youtube & 9513.0  \\ \hline
  & Popular Youtube   & 8335.4  \\ \hline
  & Twitch.tv         & 11397.1 \\ \hline
  & Soundcloud        & -       \\ \hline
3 & Unpopular Youtube & 9840.6  \\ \hline
  & Popular Youtube   & 7260.2  \\ \hline
  & Twitch.tv         & 11274.2 \\ \hline  
  & Soundcloud        & -       \\ \hline
\end{tabular}

\subsubsection{Discussions}
Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced. The Youtube web page  gets served at a much lower ping than the actual content, suggesting that the web page is being cached within UCT's network. Also note the difference in throughput for the unpopular Youtube video on the first run to the other runs. On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a far lower throughput than on subsequent or than the popular Youtube video.

Another point of particular interest is the very low ping and hop counts that appear in test case 2. The results show the test machine's IP as the IP that the content was being retrieved from. This is most likely a bug in our tool's parsing of tcpdump's output.
